---
title: "p8130_hw6_yy3439"
output: github_document
date: "2023-12-02"
---
# Problem 2

```{r}
library(tidyverse)
library(ggplot2)
set.seed(1)

#download data
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

## Step 1: Fit the Regression Line

```{r}
fit = lm(tmax ~ tmin + prcp, data = weather_df)
```
## Step 2: Bootstrapping

Firstly, create a bootstrapping function.

```{r}
boot_sample = function(df){
  sample_frac(df, replace = TRUE)
}
```

Then, we create 5000 bootstrapping samples by using a list column. 

```{r}
boot_straps = 
  tibble(strap_number = 1:5000)|>
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = weather_df))
  )

boot_straps
```

### Step 2.1: 95% Confidence Interval for $\hat{r^{2}}$

In addition, for each bootstrap sample, produce estimates of the two desired quantities.

```{r}
bootstrap_results = 
  boot_straps |> 
  mutate(
    models = map(strap_sample, \(df) lm(tmax ~ tmin + prcp, data = df) ),
    results = map(models, broom::glance)) |> 
  select(-strap_sample, -models) |> 
  unnest(results) 

# identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for estimated r^2
r_squared = bootstrap_results |> 
  summarize(
    lower_r_squared = quantile(r.squared, 0.025),
    upper_r_squared = quantile(r.squared, 0.975)) |> 
  knitr::kable(digits = 3)
```
Therefore, the 2.5% and 97.5% quantiles to provide a 95% confidence interval for estimated $\hat{r^{2}}$ is approximately 0.889 and 0.941. In another word, we're 95% confident that the true estimated r^2 lies between 0.889 and 0.941. 


### Step 2.2: Plot the Distribution of $\hat{r^{2}}$

```{r}
bootstrap_results|>
  ggplot(aes(x = r.squared)) +
  geom_density(fill = "blue") +
  theme_minimal() +
  labs(
    title = "Estimated R-Squared Distribution Plot",
    x = "estimated r-squared",
    y = "density"
  )
```
Based on the density plot of estimated r-squared, we can see that the distribution is slightly left-skewed and most of the data points gathered around 0.91 to 0.92. Based on the definition of r_squared, we can say that, for most of the bootstrapping samples, large percent of the variability in the outcome can be explained by the regression model. As a result, this indicates that our model is in goodness of fit if we assess solely based on the r-squared distribution. 

### Step 2.3: $\log(\hat{\beta_0}*\hat{\beta_1})$
